On verifying AhirV2 generated VHDL using software testbenches

### 2011-07-15 v2/CtestBench/docs/CtestBench.tex
fixed some bugs in offset calculation.

We assume that you have a {\bf Release} directory of the AhirV2 flow
installed.   The Release/bin subdirectory contains the binaries for
the translation of LLVM-byte-code down to a VHDL description. 
The Release/vhdl directory contains VHDL library elements that 
are instantiated in this VHDL description.  The Release/CtestBench 
directory contains the libraries and headers that you will need.  
Please see Release/CtestBench/examples/helloworld for an 
illustration of the whole flow.
\end{document}

>>>>

\end{document}
